---
title: "Welcome!!"
subtitle: "Interdisciplinary Curiosity as a Path to Inclusion<br/>Lunch Discussion"
author: ""
date: "Spring 2026"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---
```{r, include=FALSE}
library(countdown)
library(xaringan)
```


<style>
.blue { color: #2C5F8D; }
.green { color: #2D8659; }
.purple { color: #7B4B94; }
.orange { color: #D97E2B; }

.remark-slide-content {
  font-size: 28px;
}

.remark-slide-content h1 {
  font-size: 50px;
  margin-bottom: 30px;
}

.remark-slide-content h2 {
  font-size: 40px;
}

.remark-slide-content h3 {
  font-size: 34px;
}

.inverse {
  background-color: #2C5F8D;
  color: #FFFFFF;
}

.inverse h1, .inverse h2, .inverse h3 {
  color: #FFFFFF;
}

.pink  { color: #E05C8A; }
</style>

# Welcome! Today we hope to...


## .blue[Build Community]

## .green[Discuss Interdisciplinary Curiosity as a Path to Inclusion]

## .purple[Eat!]

---

# Agenda

**1. Introductions 1** (5 minutes)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Faculty/Staff and Students .purple[**separate**]

**2. Discussion 1** (15 minutes)

**3. Introductions 2** (5 minutes)  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp; Faculty/Staff and Students .purple[**combined**]

**4. Discussion 2** (15 minutes)

**5. Wrap-up**  (5 minutes)

---

# Ground Rules
### (discuss with your table before you begin introductions, make any desired changes)

- Acknowledge

- Accountability

- Respect

- Individual Experience

- Trust

- Share the Air

---

# Introductions

**01** Name & Pronouns (if desired)

**02** Department Affiliation & Class Year (for students)

**03** .purple[Pick from the introduction (purple) jar!]

```{r countdown-1min, echo=FALSE}
countdown(minutes = 5)
```
---

# Discussion from Topic Jar

- Pull a question from the .green[**green jar**] and read to the group

- Respond/discuss as a group

- When conversation dies down, start again!

**Suggested time per question:** 3-5 minutes

```{r countdown-15min, echo=FALSE}
countdown(minutes = 15)
```
---

# Final Question

**On a .blue[BLUE] index card: (one per table)**

What programs/opportunities would improve your sense of interdisciplinary belonging at Carleton?

**On a .pink[PINK] index card: (one per person)**

1. What was something that stuck out to you from this event?

2. Any ideas for improvement of this event?

```{r countdown-3min, echo=FALSE}
countdown(minutes = 5)
```

---
# Wrap-up

- **Sense of consensus:** Briefly, let's go around the room to hear what makes your discipline(s) feels like home?

- We will formalize materials from this and other lunches to post publicly soon!
---


class: center, middle, inverse

# Thank you for coming!